\thispagestyle{empty}
\section*{Abstract} % English
Business Process Management is a field in operations management that focuses on the management and optimisation of business processes in a company. Those business processes are often documented using both formal diagram languages and informal textual descriptions and inconsistencies between both often happen. The aim of this project is to develop an algorithm that, by using Natural Language Processing techniques, can provide a similarity metric between a textual description and a formal description in the BPMN notation of a business process.

The developed algorithm is capable of calculating a normalized similarity score based on the linguistic and structural features of both the formal model and the textual description. The algorithm has proven to be able to correctly match heterogeneous model and text pairs with high confidence.  

\section*{Resum} % Català

El \emph{Business Process Management} és un camp en l'administració de la producció que té per objectiu la gestió i optimització dels processos de negoci en una empresa. Aquests processos de negoci moltes vegades es documenten utilitzant llenguatges formals en forma de diagrama i descripcions textuals informals al mateix temps. En aquest escenari, és habitual l'aparició d'inconsistències entre les dues representacions. L'objectiu d'aquest projecte és desenvolupar un algorisme que, utilitzant tècniques de \emph{Natural Language Processing}, pugui obtenir una mesura de similitut entre una descripció textual i una formal en la notació BPMN d'un procés de negoci.

L'algorisme desenvolupat és capaç de calcular una puntuació de similitut normalitzada basada en les característiques linguístiques i estructurals del model formal i la descripció textual. S'ha demostrat que l'algorisme pot agrupar parelles heterogènies de textos i models amb un alt nivell de confiança.

\section*{Resumen} % Castellano

El \emph{Business Process Management} es un campo dentro de la administración de la producción que tiene como objetivo la gestión y optimización de los procesos de negocio en una empresa. Estos procesos de negocio muchas veces se documentan utilitzando, a la vez, lenguages formales en forma de diagrama y descripciones textuales informales. En un escenario como éste, es habitual la aparición de inconsistencias entre las dos representaciones. El objetivo de este proyecto es desarrollar un algoritmo que, utilizando técnicas de \emph{Natural Language Processing}, pueda obtener una medida de similitud entre una descripción textual y una formal en la notación BPMN de un proceso de negocio.

El algoritmo desarrollado puede calcular una puntuación de similitud normalizada basada tanto en las características linguísticas como estructurales del texto y el modelo. Se ha demostrado que el algoritmo puede agrupar parejas heterogenias tanto de texto
The developed algorithm is capable of calculating a normalized similarity score based on the linguistic and structural features of both the formal model and the textual description. The algorithm has proven to be able to correctly match heterogeneous model and text pairs with high confidence.  

\clearpage
